Quantitative Benchmarking for Theory Exploration

### 2017-08-07 TEBenchmarkPaper/article.tex
Rename benchmark paper

\title{An Approach to Benchmarking Conjecture Generators}
\author{
        Chris Warburton \\
                University of Dundee\\
}
\date{\today}

\documentclass[12pt]{article}

@@

\begin{document}
\maketitle

\begin{abstract}

\end{abstract}

\begin{displayquote}
  There is frequently more to be learn'd from the unexpected questions of a
  child than the discourses of men.
  \attrib{--- John Locke}
\end{displayquote}

\section{Introduction}

The field of mathematics has been transformed by the introduction of computers:
calculations are now routinely automated, allowing humans to focus their efforts
on higher-level, more creative activities like proving theorems; \emph{automated
theorem proving} (ATP) seeks to automate this process too, and was one of the
first tasks studied in the field of artificial intelligence
\cite{newell1956logic, sutcliffe2001evaluating}. Despite this effort, ATP
methods are not widely used by traditional mathematicians, although they have
seen use in applied areas such as hardware and software verification
\cite{Moore:2003}.

@@

One way to make these subjective, ambiguous properties more concrete is to
choose a well-studied theory, with a set of existing theorems that are deemed to
be useful or important in some way, and treat these as a \em{ground truth}
against which we can compare conjectures generated from the same theory.

@@

\section{Existing Evaluations}\label{previous approaches}

Theory exploration tools such as IsaCoSy \cite{Johansson.Dixon.Bundy:conjecture-generation}, QuickSpec and IsaScheme have been evaluated using the standard library of the Isabelle theorem prover as their ground truth.

@@

\section{Evaluation}

\includegraphics{bucketing-graph}

>>>>

% Derived from the template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\begin{filecontents*}{example.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.

@@

% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

\title{Quantitative Benchmarking for Theory Exploration%\thanks{Grants or other notes
%about the article that should go on the front page should be
%placed here. General acknowledgments should be placed at the end of the article.}
}
% \subtitle{Do you have a subtitle?\\ If so, write it here}

% \titlerunning{Short form of title}        % if too long for running head

\author{Chris Warburton% \and
                %Second Author % etc
}

% \authorrunning{Short form of author list} % if too long for running head

\institute{C. Warburton \at
              University of Dundee \\
              \email{cmwarburton@dundee.ac.uk}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
           %\and
           %S. Author \at
           %   second address
}

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

\maketitle

\begin{abstract}
Insert your abstract here. Include keywords, PACS and mathematical
subject classification numbers as needed.
\keywords{First keyword \and Second keyword \and More}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

\section{Introduction}
\label{intro}
The field of mathematics has been transformed by the introduction of computers:
calculations are now routinely automated, allowing humans to focus their efforts
on higher-level, more creative activities like proving theorems; \emph{automated
theorem proving} (ATP) seeks to automate this process too, and was one of the
first tasks studied in the field of artificial intelligence
\cite{newell1956logic,sutcliffe2001evaluating}. Despite this effort, ATP
methods are not widely used by traditional mathematicians, although they have
seen use in applied areas such as hardware and software verification
\cite{Moore:2003}.

@@

One way to make these subjective, ambiguous properties more concrete is to
choose a well-studied theory, with a set of existing theorems that are deemed to
be useful or important in some way, and treat these as a \emph{ground truth}
against which we can compare conjectures generated from the same theory.

@@

\section{Existing Evaluations}
\label{sec:previous}

Theory exploration tools such as
IsaCoSy~\cite{Johansson.Dixon.Bundy:conjecture-generation}, QuickSpec and
IsaScheme have been evaluated using the standard library of the Isabelle theorem
prover as their ground truth.

@@

\section{Evaluation}
\label{sec:evaluation}

%\includegraphics{bucketing-graph}

\begin{acknowledgements}
We are grateful for Jianguo Zhang
\end{acknowledgements}
